Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-10 main.tex
pictues on: success rates on mem-constrained cluster, memory usage by algorithm, makespan boxplots for larger cluster with invalid and only valid values. Almost zero text yet
temp, reorganizing

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, having different memory sizes per CPUs makes it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related \hmey{You may want to add other refs not from us} work~\cite{gou2020partitioning,DBLP:conf/icpp/KulaginaMB24}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}~\cite{liu2018survey}, 
    which acts as proxy for the total execution time of a workflow.

    A seminal list scheduling heuristic for workflows on heterogeneous platforms is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority; and (ii) the tasks in a priority-ordered list are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next on the processor
    where it would complete its execution first. 
    HEFT has been extended (e.g., by Shi and Dongarra~\cite{SHI2006665}) and adjusted 
    for a variety of different scheduling problem formulations. 
    Yet, none of them adhere to memory constraints as we propose -- see discussion of related work
    in Section~\ref{sec:related-work}. 
%    (\skug{check in related work if true!}).
%        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

@@

    \section{Related work: \skug{Full: 5, Polished: 4}}
    \label{sec:related-work}

    \hmey{Question: Does it make sense to place related work before the model (which is more common)?}

    We discuss relevant scheduling approaches that reuse processors or respect the memory requirements of the processors.

    \subsection{Early list schedulers with unlimited processors}
    An entire cluster of works on list schedulers has been carried out as early as the 90s.
    They all assume a DAG-shaped workflow with makespan weights on tasks, and an unlimited amount of homogeneous processors
    with the speed of 1~\cite{benoit2013survey}.\hmey{needs refs or at least a survey pointer}
    \skug{actually, Anne cited them, so citing her :-)}

    The \textit{task duplication}-based approaches exploit that sometimes running a task twice on different machines can
    help reduce the makespan by saving communication costs.
    The two categories are scheduling with partial duplication~(SPD), and with full duplication~(SFD).
    For a join task (a task whose incoming degree is larger than its outgoing degree), SPD finds a critical immediate
    parent (the one that gives the largest start time to the join task) and duplicates only it.
    SFD duplicates all parents of a join node.
    The algorithm by~\cite{dfrn1997} duplicates first (creates copies of all parent tasks) and then reduces (removes) the ones that can be removed without harming the makespan.
    The critical path fast duplication algorithm CPFD~\cite{5727760} classifies tasks into three categories: critical
    path task, in-branch task, or out-branch task.
    It schedules critical path tasks first, then in-branch tasks.
    \hmey{I'm missing the connection to our paper. Or vice versa, how is our contribution
    connected to these works? (Einordnung in den Forschungskontext) For example, do we do similar things? Are there interesting limitations we overcome?}

    Linear clustering~\cite{KWOK1999381} acts on critical paths in the workflow.
    It assigns the current critical path to one processor, removes all these tasks from the workflow, recomputes the critical
    path and repeats the procedure.
    Heaviest node first~\cite{SHIRAZI1990222} assigns the tasks level by level;
    in each level, it schedules the one with largest computation time first.

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/MsRelations}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

>>>>

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, having different memory sizes per CPUs makes it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related %\hmey{You may want to add other refs not from us} 
    work~\cite{gou2020partitioning,He21,DBLP:conf/icpp/KulaginaMB24}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}~\cite{liu2018survey}, 
    which acts as proxy for the total execution time of a workflow.

    While previous work with memory constraints has been focusing on partitioning the graph, 
    and not reusing processors during execution, 
    a seminal list scheduling heuristic for workflows on heterogeneous platforms, without accounting
    for the memory constraint, is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority; and (ii) the tasks in a priority-ordered list are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next on the processor
    where it would complete its execution first. 
    HEFT has been extended (e.g., by Shi and Dongarra~\cite{SHI2006665}) and adjusted 
    for a variety of different scheduling problem formulations. 
    Yet, none of them adhere to memory constraints as we propose -- see discussion of related work
    in Section~\ref{sec:related-work}. 
%    (\skug{check in related work if true!}).
%        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

@@

    \section{Related work} %: \skug{Full: 5, Polished: 4}}
    \label{sec:related-work}

   First, we focus on HEFT-like scheduling heuristics from the literature  that do not necessarily  
   consider memory constraints. Then, we discuss memory-aware scheduling algorithms. 
   Finally, we move to related work on dynamic or adaptive algorithms. 
 %   \hmey{Question: Does it make sense to place related work before the model (which is more common)?}

%    We discuss relevant scheduling approaches that reuse processors or respect the memory requirements of the processors.
%
%    \subsection{Early list schedulers with unlimited processors}
%    An entire cluster of works on list schedulers has been carried out as early as the 90s.
%    They all assume a DAG-shaped workflow with makespan weights on tasks, and an unlimited amount of homogeneous processors
%    with the speed of 1~\cite{benoit2013survey}.\hmey{needs refs or at least a survey pointer}
%    \skug{actually, Anne cited them, so citing her :-)}
%
%    The \textit{task duplication}-based approaches exploit that sometimes running a task twice on different machines can
%    help reduce the makespan by saving communication costs.
%    The two categories are scheduling with partial duplication~(SPD), and with full duplication~(SFD).
%    For a join task (a task whose incoming degree is larger than its outgoing degree), SPD finds a critical immediate
%    parent (the one that gives the largest start time to the join task) and duplicates only it.
%    SFD duplicates all parents of a join node.
%    The algorithm by~\cite{dfrn1997} duplicates first (creates copies of all parent tasks) and then reduces (removes) the ones that can be removed without harming the makespan.
%    The critical path fast duplication algorithm CPFD~\cite{5727760} classifies tasks into three categories: critical
%    path task, in-branch task, or out-branch task.
%    It schedules critical path tasks first, then in-branch tasks.
%    \hmey{I'm missing the connection to our paper. Or vice versa, how is our contribution
%    connected to these works? (Einordnung in den Forschungskontext) For example, do we do similar things? Are there interesting limitations we overcome?}
%
%    Linear clustering~\cite{KWOK1999381} acts on critical paths in the workflow.
%    It assigns the current critical path to one processor, removes all these tasks from the workflow, recomputes the critical
%    path and repeats the procedure.
%    Heaviest node first~\cite{SHIRAZI1990222} assigns the tasks level by level;
%    in each level, it schedules the one with largest computation time first.

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/MsRelations2}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

    \paragraph{Memory Usage}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
        \caption{Memory usage by algorithm by workflow size. Includes invalid heft schedules}
        \label{fig:mem-usages}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
        \caption{Memory usage by algorithm by workflow size. Includes only valid heft schedules}
        \label{fig:mem-usages-onlyvalid}
        \vspace{-0.3cm}
    \end{figure}

    \paragraph{Memory-constrained cluster}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/success-rates-tiny}
        \caption{Success ratey by algorithm by workflow size. Taller is better. }
        \label{fig:success-rates-tiny}
        \vspace{-0.3cm}
    \end{figure}
